Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-09-25 head.tex
just begin

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In the Cloud Manufacturing Ecosystem, a benign mode and scheduling methodology for massive services, which were contructed by resources is required, in order for the collaboration within the whole Industry Chain.
This paper 
\begin{inparaenum}[1)]
\item studied the features of the resources and services, then proposed a mode of Cloud Manufacturing;
\item modeled the services scheduling matter in the chain;
\item designed a simulation for the Cloud Manufacturing Ecosystem;
\item opened some Ecosystem related issues. 
\end{inparaenum}
With the use of Big-Data analysis on the Cloud Platform, resource optimization assessment/schedule methods could be developed, which could
gradually evolve the ecosystem to an optimal situation.

>>>>

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In the Cloud Manufacturing Ecosystem, a benign mode and scheduling methodology for massive services, which were constructed standardly by resources is required, in order for the collaboration within the whole Industry Chain.
This paper 
\begin{inparaenum}[1)]
\item studied the features of the resources and services, then proposed a mode of Cloud Manufacturing;
\item modeled the services scheduling matter in the chain;
\item designed a simulation for the Cloud Manufacturing Ecosystem;
\item opened some Ecosystem related issues. 
\end{inparaenum}
With the use of Big-Data analysis on the Cloud Platform, resource optimization assessment/schedule methods could be developed, which could
gradually evolve the ecosystem to an optimal situation.
